\startcomponent c_10_safety_s2_095-en
\product prd_ba_s2_095-en

\marking[chapter]{Safety symbols}


\chapter{Safety symbols}

\setups[pagestyle:marginless]


\section{New European hazard pictograms}

{\em Rhombus||shaped box with white background and red
border.}\par\blank[1*medium]
{\em The CLP Regulation\index{CLP Regulation} entered into force in the EU in 2008 and stipulates new hazard pictograms for hazardous substances and products.}\par\null

\startSymList \GHSgeneric
\SymList
 \textDescrHead{Caution}
 Warns about\index{Health hazard} health hazards that will not result in death or serious damage to health. Such hazards include skin irritancy/sensitization and the triggering of an allergy. This symbol is also used as a warning against other hazards such as flammability.\par
 Replaces:\crlf \HAZOcross\ and \HAZOpoison\ and \PHgeneric
\stopSymList

\startSymList \GHSbody
\SymList
 \textDescrHead{Serious health hazard; can also cause death, particularly in children}
 Products may cause serious damage to health. This symbol also warns about hazards\index{Hazard+Pregnancy} during pregnancy, carcinogenicity\index{Hazard+Carcinogenic substances} and similar serious health hazards. Products are to be used with care.\par
 Replaces:\crlf \HAZOcross\ and \HAZOpoison\
\stopSymList

\startSymList \GHSbomb
\SymList
 \textDescrHead{Heating may cause an explosion}
 During a reaction, unstable explosive\index{Hazard+Explosion} substances, mixtures and products containing explosive substances\index{Explosive substances} exhibit violent expansion that can result in considerable destructive effects; if handled inappropriately there is a danger to life.\par
 Replaces:\crlf \HAZObomb\
\stopSymList


\startSymList \GHSpoison
\SymList
 \textDescrHead{Toxic}
 Products\index{Hazard+Toxic} can result in serious or even fatal poisoning when ingested, even when only a small amount is absorbed through the skin, inhaled\index{Toxic substances} or swallowed. Do not allow direct contact.\par
 Replaces:\crlf \HAZOpoison\
\stopSymList

\startSymList \GHSfire
\SymList
 \textDescrHead{Highly flammable}
 Products\index{Hazard+Fire} ignite easily when near heat or flames. Sprays marked with this pictogram must not be sprayed onto hot surfaces or near naked flames under any circumstances.\par
 Replaces:\crlf \HAZOfire\ and \HAZOfirebis\
\stopSymList

\startSymList \GHSenvironment
\SymList
 \textDescrHead{Dangerous to the environment and aquatic life}
 Products\index{Environmental protection} may cause short- or long||term damage to the environment\index{Toxic substances}. They may kill aquatic life (\eG\ fish) or cause long||term damage to the environment. Never dispose of in wastewater or household waste!\par
 Replaces:\crlf \HAZOenvironment\
\stopSymList

\startSymList \GHScorrosive
\SymList
 \textDescrHead{Corrosive}
 Products\index{Hazard+Skin injury}\index{Hazard+Eye injury} may damage skin or cause scarring even after brief contact or permanently damage the eyes. Protect skin and eyes when using the product!\par
 Replaces:\crlf \HAZOcross\ and \HAZOcorrosive
\stopSymList

\page [yes]


\section{Warning symbols}

{\em Pictogram in black on a yellow background}\par\null

\startSymList \PHgeneric
\SymList
 \textDescrHead{General warning symbol}
 Indicates\index{Hazard+General}\index{Warning symbol} a direct hazard risk that could result in injury to you or others.
 \crlf\null
\stopSymList

\startSymList \PHpoison
\SymList
 \textDescrHead{Warning about toxic substances}
 Toxic substances\index{Hazard+Poisoning} ingested through skin contact, inhalation or swallowing could result in severe acute or chronic health problems or even death.
\stopSymList

\startSymList \PHfire
\SymList
 \textDescrHead{Warning about substances that pose a fire hazard}
 Avoid naked flames and sparks\index{Hazard+Fire}. Substance is highly flammable or can accelerate a fire. No smoking!
\stopSymList

\startSymList \PHexplosive
\SymList
 \textDescrHead{Warning about substances that pose an explosion hazard}
 Solid, liquid or gel||like substances\index{Hazard+Explosion} or preparations that may explode when exposed to impact, friction, fire, heat, etc. No smoking!
\stopSymList

\startSymList \PHcrushing
\SymList
 \textDescrHead{Warning about crush hazard}
 Indicates an area\index{Hazard+Crushing} where moving mechanical parts present a crush hazard. Keep away from this area when the apparatus is switched on.
\stopSymList

\startSymList \PHhand
\SymList
 \textDescrHead{Warning about hand injury}
 There is a risk that\index{Hazard+Crushing} hands or other body parts\index{Hazard+Hand injury} could be crushed \eG\ while tipping the driver’s cabin or dump bed.
\stopSymList

\startSymList \PHentangle
\SymList
 \textDescrHead{Warning about counter||rotating rollers / entanglement hazard}
 There is a risk that limbs\index{Hazard+Entanglement} could become caught and entangled in rotating parts. Keep clear while the apparatus is switched on.
\stopSymList

\startSymList \PHcorrosive
\SymList
 \textDescrHead{Warning about corrosive substances}
 Handle with\index{Hazard+Corrosive substances} care, wear appropriate personal protective equipment (gloves, protective goggles, protective clothing).
\stopSymList

\startSymList \PHhot
\SymList
 \textDescrHead{Warning about hot surfaces}
 Do not get close to the part or apparatus\index{Hazard+Burn} unless you have adequate knowledge; wear gloves.
\stopSymList

\startSymList \PHvoltage
\SymList
 \textDescrHead{Warning about hazardous electrical voltage}
 Do not touch with metal\index{Hazard+Electrical voltage} objects. Risk of injury and fire in the event of a short circuit.
\stopSymList

\startSymList \PHfalling
\SymList
 \textDescrHead{Warning about fall hazard}
 Take particular care in this area\index{Hazard+Fall}, wear appropriate footwear (with non||slip, hydrocarbon||resistant soles).
\stopSymList

\startSymList \PHbattery
\SymList
 \textDescrHead{Warning about hazard relating to batteries} Indicates hazards associated with the charging of batteries (lead||acid battery)\index{Hazard+Battery}, particularly caused by hydrogen gas leakages and the sulfuric acid contained in the batteries.
\stopSymList

\startSymList \PHremote
\SymList
 \textDescrHead{Warning about automatic startup}
 Warns about\index{Hazard+Automatic startup} the potential risk that an apparatus could be started automatically or remotely.
\stopSymList

% \startSymList \PHquetschgefahr
% \SymList
% \textDescrHead{Risque d’écrasement}
% Risque d’écrasement\index{risque d’écrasement}.
% \stopSymList
% % NOTE: Doppelt! (auch Bilddatei)
%
% % NOTE: Evtl. Folgendes als Ersatz für oben?

% \startSymList\PHhandcrushed
% \SymList
 % \textDescrHead{Gefahr von Handquetschungen}
 % Es besteht\index{Gefahr+Quetschung} die Gefahr, dass Hände oder Finger
 % gequetscht werden. Nähern Sie die Hände nicht an, ohne die Gefahr
 % identifiziert und beseitigt zu haben.
% \stopSymList

\startSymList \PHhandfoot
\SymList
\textDescrHead{Warning about moving parts}
Warning\index{Hazard+Moving parts} about moving machine/vehicle parts.
\stopSymList

\startSymList \PHnarrowed
\SymList
 \textDescrHead{Warning about narrowed roadway}
 Narrowed\index{Hazard+Vehicle width} roadway.
 % Denken Sie an die Breite des Fahrzeugs.
\stopSymList

\page [yes]


\section{Prohibitive symbols}

{\em Circular pictogram with white background and red border and diagonal line}
\par\null


\startSymList \PPfire
\SymList
 \textDescrHead{Fire, naked flames and smoking forbidden} Naked flames\index{Forbidden+Smoking, flames} and glowing embers of any sort are forbidden (\eG\  burning cigarette, match, candle; same applies to sparks/sparking of any type).
\stopSymList

\startSymList \PPentry
\SymList
 \textDescrHead{No access to unauthorized persons}
 Unauthorized\index{Forbidden+Access} persons are not permitted to enter or get close to this area.
\stopSymList

\startSymList \PPphone
\SymList
 \textDescrHead{Switch off your phone}
 Cellphones\index{Forbidden+Cellphones} and any other device that emits electromagnetic radiation must be switched off. Electromagnetic radiation can interfere with equipment electronics.
\stopSymList

\startSymList \PPspray
\SymList
 \textDescrHead{Do not spray with water}
 Never direct a jet of water or steam\index{Forbidden+Water jet, steam} at sensitive parts and equipment (\eG\ sensors, control units, injection systems, etc.).
\stopSymList

\startSymList \PPchildren
\SymList
 \textDescrHead{Keep away from children}
 Denotes\index{Forbidden+Children} a particularly high risk for children. In general, children should not be allowed near an active machine, not even during maintenance work.
\stopSymList

\startSymList \PPwater
\SymList
 \textDescrHead{Not drinking water}
 Do not drink water\index{Forbidden+Not drinking water} from the tank. There is a risk of poisoning.
\stopSymList

% \page [yes]


\section{Environmental protection symbols}

\startSymList \PSrecycle
\SymList
 \textDescrHead{Recycling}
 Specific directions for ensuring certain types of waste are disposed of properly.
\stopSymList

\startSymList \PSwelt
\SymList
 \textDescrHead{Environmental protection}
 Reference to applicable environmental protection regulations.
\stopSymList

\startSymList \PStrash[width=\PictoHeight,height=,]
\SymList
 \textDescrHead{Dispose of waste in accordance with regulations}
 Special disposal regulations apply to certain types of waste \eG\ lead||acid batteries.
\stopSymList


\testpage[12]


\section{Instruction symbols}


{\em Circular pictogram with blue background}\par\null

\startSymList \PMgeneric
\SymList
 \textDescrHead{General instruction symbol}
 This symbol must be used in conjunction with another symbol that specifies the instruction.
\stopSymList


\startSymList \PMrtfm
\SymList
 \textDescrHead{Observe user instructions}
 Users must read the instructions relating to issues, equipment or products marked with this symbol\index{User instructions, read} before starting up. The user instructions must be stored close to hand in the driver’s cabin.
\stopSymList

\startSymList \PMproteyes
\SymList
 \textDescrHead{Wear eye protection}
 Eye protection must be worn when undertaking work that presents a risk of eye injury\index{Eye protection}.
\stopSymList

\startSymList \PMprothands
\SymList
 \textDescrHead{Wear hand protection}
 Hand protection must be worn when undertaking work that presents a risk of hand injury\index{Hand protection, use}.
\stopSymList

\startSymList \PMprotears
\SymList
 \textDescrHead{Use ear protection}
 Ear protection must be worn\index{Hazard+Hearing} (\eG close to a fan or turbine that is running).
\stopSymList

\startSymList \PMsafetybelt
\SymList
 \textDescrHead{Wear a safety belt} Wear\index{Safety belt} your safety belt for your own safety.
\stopSymList

\section{Other symbols}

% \adaptlayout[height=+5mm]{{{

% \startSymList \SETshoe
% \SymList
% \textDescrHead{Port de chaussures de sécurité obligatoire}
% Le port de chaussures de sécurité est obligatoire\index{chaussures de sécurité}.
% \stopSymList
%
% \startSymList \SETglasses
% \SymList
% \textDescrHead{Port de lunettes des protection obligatoire}
% Le port de lunettes est obligatoire\index{lunette de protection}.
% \stopSymList
%
% \startSymList \SEToreillettes
% \SymList
% \textDescrHead{Port de casque obligatoire}
% Le port d’un casque de protection est \index{casque} obligatoire.
% \stopSymList
%
% \startSymList \SETgloves
% \SymList
% \textDescrHead{Port de gants de protection obligatoire}
% Le port de gants de protection est obligatoire\index{gants}.
% \stopSymList
%
% \startSymList \SETmainecrase
% \SymList
% \textDescrHead{Risque d’écrasement}
% Danger pour les mains\index{écrasement} et les pieds.
% \stopSymList
%
% \startSymList \SETgetriebe
% \SymList
% \textDescrHead{Risque de happement}
% Risque de happement par\index{happement} des pièces en rotation.
% \stopSymList
%
% \startSymList \SETradkeil
% \SymList
% \textDescrHead{Cale de roue}
% Sécuriser le véhicule contre toute mise\index{Cale de roue} en marche involontaire.
% \stopSymList
%}}}

\startSymList \SETfirstaid
\SymList
\textDescrHead{First aid}
 Indicates where the first||aid box is stored. A key aspect of first aid is to contact the emergency services as quickly as possible.\index{First aid}\index{Emergency call} Enter your emergency services numbers here:
 \fillinrules[n=1]{\bf
 \framed[align=right,frame=off,offset=none,width=30mm]{Medical services}}
\fillinrules[n=1]{\bf
\framed[align=right,frame=off,offset=none,width=30mm]{Police}}
\fillinrules[n=1]{\bf
\framed[align=right,frame=off,offset=none,width=30mm]{Fire service}}
\stopSymList

\startSymList \SETbrandschutzzeichen
\SymList
\textDescrHead{Fire extinguisher}
 Certain machines are equipped with one or more fire extinguishers\index{Fire extinguisher}. These usually require specialist maintenance work. Further information on this work can be found on the device or in the user instructions for the device.
\stopSymList


\page[yes]

\section{The three steps in getting help}
% NOTE [tf]: Shouldn't be in this book, IMO

\starttextbackground [CB]
\textDescrHead{Ensure the scene of the incident and the people affected are safe}
\startitemize
\item Assess how safe the situation is and ensure there is no
additional danger
\stopitemize
\textDescrHead{Assess the condition of those who are injured}
\startitemize
\item Determine whether they are conscious and breathing normally. If necessary, clear their airway.
\stopitemize
\textDescrHead{Contact the emergency services}
\startitemize You must provide the following information when you make your call:\par
 \item The telephone number you can be reached on.
 \item The nature of the incident (illness, accident).
 \item Any hazards that are present (fire, explosion, building collapse, etc.).
 \item The precise location of the incident.
 \item The number of people injured and their condition.
 \item Any measures that have already been taken to help those affected.
 \item Answer any other questions that you are asked.
\stopitemize
\stoptextbackground

\stopcomponent


